\documentclass[12pt]{article}

\usepackage[left=1in,right=1in,top=0.7in,bottom=1in]{geometry}

\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
\newcommand{\Hrule}{\rule{\linewidth}{0.3mm}}

\linespread{0}

\usepackage{parskip}
\setlength{\parskip}{1pt}

\makeatletter% since there's an at-sign (@) in the command name
\renewcommand{\@maketitle}{
  \parindent=0pt% don't indent paragraphs in the title block
  \begin{center}
    \MakeUppercase{\large \bf \@title \vspace{10pt}}
    \HRule%
  \end{center}%
  \vspace{5pt}
  \textit{\@author \hfill \@date}
  \par
}
\makeatother % resets the meaning of the at-sign (@)

\def \tit1{Science Definitions}
\def \auth1{Darrin Tyler Schultz}
\def \prog1{Descriptions of Interesting Things}

\title{\tit1}
\author{\auth1}
\date{\prog1}

\begin{document}

\maketitle % prints the title block
\vspace{8pt}

\begin{enumerate}
\item \textbf{DNA Barcoding on Bacteria: A Review.} Lebonah et al,
  2014. This review was mostly just useful as a launching point for
  finding other articles related to bacterial phylogeny.
\begin{itemize}
\item \textbf{Barcoding bamboozled by bacteria: convergence to
    metazoan mitochondrial primer targets by marine microbes.} Siddall
  et al, 2009. Use of degenerate primers and reducing annealing
  temperatures to use COI on many organisms. Special primers for Euks,
  for molluscs. Often times though these primers end up amplifying
  bacterial regions. So, if we amplify using COI, then there could be
  a lot of problems with contamination or amplifying bacterial targets
  on accident.
\item \textbf{An emergent science on the brink of irrelevance: A
    review of the past 8 years of DNA barcoding.} Taylor and Harris 2012
\item \textbf{Microbial diversity in the deep sea and the
    underexplored 'rare biosphere'.} Sogin et al 2006
\item \textbf{Two new computational methods for universal DNA
    barcoding: a benchmark using barcode sequences of bacteria,
    archaea, animals, fungi, and land plants.} Tanabe and Toju 2013
\item \textbf{Molecular systematics: counting angels with DNA} Mark 2003
\item \textbf{Impact of culture-independent studies on the emerging
    phylogenetic view of bacterial diversity.} Hugenholtz et al 1998
\item \textbf{A phylogeny-driven genomic encyclopedia of Bacteria and
    Archaea} Wu et al 2009
\end{itemize}
\end{enumerate}
\vspace*{\fill}
 \begin{center}
 \textit{\auth1}

 \textit{\prog1}
\end{center}

\end{document}